\section{Statistics}

\subsection{Permutations and Combinations}

The permutation and combination commands are provided by \verb|\perm| and \verb|\comb| respectively. The two functions share the following syntax:

\begin{myframe}{Syntax}
    \verb|\foo{<n>}{<r>}|
    \begin{itemize}
        \item \verb|{<n>}| (mandatory): Total number of objects.
        \item \verb|{<r>}| (mandatory): Number objects to permute/choose.
    \end{itemize}
\end{myframe}

\begin{myframe}{Examples}
    \begin{itemize}
        \item \verb|$\perm{10}{5}$| \produces{} $\perm{10}{5}$.
        \item \verb|$\comb{10}{5}$| \produces{} $\comb{10}{5}$.
    \end{itemize}
\end{myframe}

\subsection{Probability, Expectation and Variance}

The probability, expectation and variance functions are provided by \verb|\P|, \verb|\E| and \verb|\Var| respectively. They are implemented using \verb|\DefCmdCond|.

\begin{myframe}{Examples}
    \begin{itemize}
        \item \verb|$\P{X = 1}$| \produces{} $\P{X = 1}$.
        \item \verb|$\E{X = 1}{Y = 1}$| \produces{} $\E{X = 1}{Y = 1}$.
    \end{itemize}
\end{myframe}

\subsection{Distributions}

\subsubsection{Binomial Distribution}

The binomial distribution is provided by \verb|\Binom|.

\begin{myframe}{Syntax \framecmd{Binom}}
    \verb|\Binom{<n>}{<p>}|
    \begin{itemize}
        \item \verb|{<n>}| (mandatory): Number of trials.
        \item \verb|{<p>}| (mandatory): Probability of success.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{Binom}}
    \begin{itemize}
        \item \verb|$\Binom{10}{0.5}$| \produces{} $\Binom{10}{0.5}$.
    \end{itemize}
\end{myframe}

\subsubsection{Poisson Distribution}

The Poisson distribution is provided by \verb|\Po|.

\begin{myframe}{Syntax \framecmd{Po}}
    \verb|\Po{<lambda>}|
    \begin{itemize}
        \item \verb|{<lambda>}| (mandatory): The mean rate of the Poisson process.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{Po}}
    \begin{itemize}
        \item \verb|$\Po{2}$| \produces{} $\Po{2}$.
    \end{itemize}
\end{myframe}

\subsubsection{Geometric Distribution}

The geometric distribution is provided by \verb|\Geo|.

\begin{myframe}{Syntax \framecmd{Geo}}
    \verb|\Geo{<p>}|
    \begin{itemize}
        \item \verb|{<p>}| (mandatory): Probability of success.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{Geo}}
    \begin{itemize}
        \item \verb|$\Geo{0.5}$| \produces{} $\Geo{0.5}$.
    \end{itemize}
\end{myframe}

\subsubsection{Uniform Distribution}

The uniform distribution is provided by \verb|\Uni|.

\begin{myframe}{Syntax \framecmd{Uni}}
    \verb|\Uni{<a>}{<b>}|
    \begin{itemize}
        \item \verb|{<a>}| (mandatory): The lower bound.
        \item \verb|{<b>}| (mandatory): The upper bound.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{Uni}}
    \begin{itemize}
        \item \verb|$\Uni{0}{1}$| \produces{} $\Uni{0}{1}$.
    \end{itemize}
\end{myframe}

\subsubsection{Exponential Distribution}

The exponential distribution is provided by \verb|\Exp|.

\begin{myframe}{Syntax \framecmd{Exp}}
    \verb|\Exp{<lambda>}|
    \begin{itemize}
        \item \verb|{<lambda>}| (mandatory): The mean rate of the Poisson process.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{Exp}}
    \begin{itemize}
        \item \verb|$\Exp{2}$| \produces{} $\Exp{2}$.
    \end{itemize}
\end{myframe}

\subsubsection{Normal Distribution}

The normal distribution is provided by \verb|\Normal|.

\begin{myframe}{Syntax \framecmd{Normal}}
    \verb|\Normal{<mean>}{<variance>}|
    \begin{itemize}
        \item \verb|{<mean>}| (mandatory): The mean.
        \item \verb|{<variance>}| (mandatory): The variance.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{Normal}}
    \begin{itemize}
        \item \verb|$\Normal{0}{1}$| \produces{} $\Normal{0}{1}$.
    \end{itemize}
\end{myframe}

\subsubsection{Student T Distribution}

The Student T distribution is provided by \verb|\StudentT|.

\begin{myframe}{Syntax \framecmd{StudentT}}
    \verb|\StudentT{<df>}|
    \begin{itemize}
        \item \verb|{<df>}| (mandatory): Degrees of freedom.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{StudentT}}
    \begin{itemize}
        \item \verb|$\StudentT{10}$| \produces{} $\StudentT{10}$.
    \end{itemize}
\end{myframe}

\subsubsection{Chi-Squared Distribution}

The $\chi^2$ distribution is provided by \verb|\ChiSq|.

\begin{myframe}{Syntax \framecmd{ChiSq}}
    \verb|\ChiSq{<df>}|
    \begin{itemize}
        \item \verb|{<df>}| (optional): Degrees of freedom.
    \end{itemize}
\end{myframe}

\begin{myframe}{Example \framecmd{ChiSq}}
    \begin{itemize}
        \item \verb|$\ChiSq{10}$| \produces{} $\ChiSq{10}$.
        \item \verb|$\ChiSq$| \produces{} $\ChiSq$.
    \end{itemize}
\end{myframe}

\subsection{Hypothesis Testing}

The null hypothesis and alternative hypothesis symbols are provided by \verb|\nullhyp| and \verb|\althyp| respectively.

\begin{myframe}{Examples}
    \begin{itemize}
        \item \verb|$\nullhyp$| \produces{} $\nullhyp$.
        \item \verb|$\althyp$| \produces{} $\althyp$.
    \end{itemize}
\end{myframe}